### 2020-09-04 paper/main.tex
add intro draft

\documentclass[acmsmall]{acmart}

\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{10.1145/1122445.1122456}

\begin{document}

\title[Towards user-friendliness in theorem provers]{Towards user-friendliness
  in proof assistants: an effect-based attempt}

\author{April Gonçalves}
\email{april@cyberglot.me}
\affiliation{
  \institution{Metastate AG}
  \city{Edinburgh}
  \state{UK}
}

\renewcommand{\shortauthors}{April Gonçalves}

\begin{abstract}
Proof assistants provide a framework for modelling and verification of
theories, as well as trust-worthy software. However, such power is usually only
available to experts. We propose a new approach, based on algebraic effects and
handlers, to integrate different automated proof strategies that enables
newcomers to take advantage of proof assistants without a more in-depth
understanding of underlying theory. Our approach gives beginner users an effect
system, a handful of effectful strategies (tactics, proof search and a SMT
solver) and their handlers under a shared interface, while advanced users can
extend our system with new effects and new handlers. Lastly, we prototype the
system as a library in Agda. While our prototype is minimal, it shows how easily
proofs can be carried on so long as the user has the correct intuition. We
believe our system empowers non-experts and has the potential to bring verified
software to many relevant industries, such as finance.
\end{abstract}

\keywords{effect handlers, proof assistants, user experience}

\maketitle

\section{Introduction}

The usability of proof assistants such as Coq, Agda, Isabelle/HOL and Twelf is
hard to measure: all of them require significant domain knowledge that
frequently matches a deeper understanding of Type Theory, the theory that
enables such assistants to exist. Coq and Isabelle/HOL are more commonly applied
outside their niche, and their programming style is sharply different from
mainstream programming and even functional programming. Granted, they come with
their own integrated development environment (IDE), which may make it easier for
students and newcomers. To our knowledge, no usability study has been
held for a proof assistant, however there exists studies that account for
an informal ``usability'' criteria -- they appear to measure how fast users can
familiarise themselves with the system or IDE.

Folklore within the proof assistants community seems to show that typical users
find Coq hard to use due to a large library of tactics and difficult readability
of the code after its completion. Many Coq learning materials suggest users to
add comments for structural induction cases and inductive hypothesis. As
mentioned, no user studies were conducted to attest such hypotheses.

It also has to be granted that proof assistants are relatively new technology
and there are no guidelines or even an intuition on how such systems should
perform or what features should be available to the users. The closest model we
have are proofs by hand, however, following that model for proof assistants has
two main pitfalls: (a) proofs by hand are also not widely taught in mathematics
classes during school years; and (b) proofs by hand and automated proof
writing employ fundamentally different paradigms, where the latter requires
axioms and formulations to be encoded explicitly, commonly known as a ``pedantic
proof style''.

\subsection{Empowering users of different levels of expertise}

To popularise software verification, we mush make proof writing less of a
burden to the user. Currently, only specialists can write proofs for their
programs, even though the working programmer understands the domain and
invariants of their projects -- otherwise they wouldn’t be able to write any
software, but usually the learning curve of automated formal proofs is steep
and considered too expensive.

In our approach, we propose an (algebraic) effects and handlers view of such
proofs, based on prior work developed by the Andromeda proof assistant. Here,
our users will program as they would normally and invoke
a proof environment as an effect to prove certain properties as they go. Given
that the proof environment is ``just'' an effect, we envision that different proof
styles (e.g, agda-style dependent types, SMT solver, proof search) can be ``composed''
under a shared interface, a proof object that can manipulate itself while
querying different automated proof engines.

The reasons we employ algebraic effects and handlers are two-fold:
\begin{enumerate}
\item as proofs cannot be fully automated, all approaches that try to automate
  the process (e.g, proof search, SMT solver) may either be non-deterministic or
  never find a solution. Therefore, the system should be able to handle
  ``impure'' computations and errors. Algebraic effects and handlers have
  well-defined semantics and provide a simple interface for performing effects.
  With them, we avoid indiscriminate effects that are often error-prone and
  intricate effects machinery such as monad transformers.
\end{enumerate}

\subsection{Main contributions}

\end{document}
\endinput

### 2020-09-07 paper/main.tex
update paper
more text and plus infographic

@@
 
-\setcopyright{acmcopyright}
-\copyrightyear{2018}
-\acmYear{2018}
-\acmDOI{10.1145/1122445.1122456}
-
+\usepackage{pdfpages}
 \begin{document}
@@
 
-\section{Introduction}
+\section{Verification for the Masses}
 
@@
 programs, even though the working programmer understands the domain and
-invariants of their projects -- otherwise they wouldn’t be able to write any
-software, but usually the learning curve of automated formal proofs is steep
-and considered too expensive.
+invariants of their projects -- otherwise they would not be able to write any
+software. \textit{Our hypothesis is that programmers are well-equipped to derive and
+prove properties of their software, but they lack the mathematical maturity and
+vocabulary to carry on a formal proof. } We have evidence that students fail to
+produce well-made proofs due to the lack of mathematical maturity, even though
+they do understand the subject matter at hand.
 
@@
 a proof environment as an effect to prove certain properties as they go. Given
-that the proof environment is ``just'' an effect, we envision that different proof
-styles (e.g, agda-style dependent types, SMT solver, proof search) can be ``composed''
+that the proof environment is \textit{just} an effect, we envision that different proof
+styles (e.g, Agda-style dependent types, SMT solver, proof search) can be ``composed''
 under a shared interface, a proof object that can manipulate itself while
@@
 
-The reasons we employ algebraic effects and handlers are two-fold:
+The reasons we employ algebraic effects and handlers are manifold:
 \begin{enumerate}
@@
   With them, we avoid indiscriminate effects that are often error-prone and
-  intricate effects machinery such as monad transformers.
+  intricate effects machinery such as monad transformers;
+\item its semantics accommodate composition of arbitrary effects and the
+  composition of multiple handlers, which means users have the ability to weaken
+  more general strategies into specific ones while maintaining the original untouched;
+\item it has well-defined semantics, and it is the main feature of many new
+  research languages, such as Koka, Eff, Frank and Effekt, what suggests a greater
+  potential to be investigated further.
 \end{enumerate}
 
-\subsection{Main contributions}
+\subsection{Goals and Contributions}
+
+The present project is still under development, and we intend to develop a core calculus and a
+full compiler-level implementation into the Juvix\footnote{Juvix is a
+  dependently-typed programming language for smart contracts. More information
+  at juvix.org} programming language.
+
+\paragraph{Goals} The project exists to enable users to write safe, verified
+code without investing time into learning dependent types and theorem proving.
+The project's goals are presented as follows:
+\begin{enumerate}
+\item make software verification more accessible to programmers familiar with
+  functional programming;
+\item foster knowledge sharing between domain experts and regular programmers;
+\item lower the barrier to entrance into software verification to non-experts.
+\end{enumerate}
+
+\paragraph{Contributions} While the project is a work-in-progress, this paper
+provides three important contributions that lays out the full extent of the
+work, which are presented as follows:
+\begin{enumerate}
+\item a specification of a user interface for automated proofs based on
+  algebraic effects and handlers that permits user-defined effects for proof
+  strategies, and also user-defined handlers for existing effects (Section \ref{intro-witch});
+\item a minimal prototype in Agda that validates the feasibility of such system
+  (Section \ref{witch-agda});
+\item a short technical account of the effort required to materialise such a
+  user interface into proof assistants (Section \ref{tech-details}).
+\end{enumerate}
+
+\section{Introducing Witch} \label{intro-witch}
+
+\begin{figure}[!ht]
+   \centering
+    \includegraphics[width=\textwidth]{image/witch.eps}
+    \caption{Low-fidelity prototype of Witch}
+    \label{fig:prototype}
+\end{figure}
+
+In this section, we introduce our tool, named Witch.
+
+\paragraph{Downsides of our approach}
+There are two main styles for writing proofs within a proof assistant: external
+verification and internal verification. The latter concerns itself with code
+that is \textit{correct-by-construction}, meaning that only valid states allowed and it
+carries all information necessary to make proofs trivial; while the former
+concerns itself with proofs about non-proof-carrying code.
+Witch's primarily focus is on external verification. We believe that newcomers
+will struggle to write proof-aware code, since it departs strongly from
+mainstream programming, even within the functional style. We expect users to
+write their code as they normally would do and then prove necessary properties.
+However, Witch does not support writing correct-by-construction code.
+
+\section{Witch in Agda} \label{witch-agda}
+
+\paragraph{Why Agda?} Agda provides high-level meta-programming constructs, and
+its coding style is a reminiscent of ML family of functional programming languages.
+
+\subsection{Technical Effort Required} \label{tech-details}
+
+Although Witch is implementable at the library level, it requires that proof
+assistants to provide a set of off-the-shelf features. The most important
+feature is type-level meta-programming. Witch is only possible given the proof
+assistant's ability to manipulate its own proof terms to generate new variables,
+holes, goals, among others and manipulate terms and types in a proof-carrying
+fashion. Secondly, the proof assistant should feature an interface with the
+outside world. Although it is not inherently a requirement, its absence means
+that no solver will be integrated, diminishing the proposed value of the tool.
+Lastly, proof assistants must support algebraic effects and handlers. If there
+is no built-in solution, a library-level solution is possible -- as we did in
+Agda. However, a solid implementation may not be trivial to achieve. In Agda,
+we translate all calls into optimised continuation-passing style that inlines
+all calls. This strategy also works at compiler-level if necessary. There are
+many strategies to efficiently implement algebraic effects and handlers, but we
+went for the one that seemed the most straight-forward method to implement it in Agda.
 

### 2020-09-11 paper/main.tex
more text and better infographic

@@
 \author{April Gonçalves}
-\email{april@cyberglot.me}
+\email{april@metastate.dev}
 \affiliation{
@@
 
-In this section, we introduce our tool, named Witch.
+In this section, we introduce our tool, named Witch\footnote{Our tool's name is
+  a play after assistant tools colloquially called ``wizards''. There is no
+  consensus of what a wizard is or what are exactly the tasks it is supposed
+  to help users. It seems to be used mostly for multiple-step and/or
+  configuration features, however. We went for the name ``witch'' to align it to
+the idea of assistant tools, while dodging an overloaded terminology.}.
 
@@
 carries all information necessary to make proofs trivial; while the former
-concerns itself with proofs about non-proof-carrying code.
+concerns itself with proofs about code that does not carry any additional
+information for proving purposes.
 Witch's primarily focus is on external verification. We believe that newcomers
@@
 write their code as they normally would do and then prove necessary properties.
-However, Witch does not support writing correct-by-construction code.
+However, Witch does not support writing correct-by-construction code. As proofs
+are erased during compilation-time in Juvix, Witch could be extended
+to be indexed by proof objects and parameterised over any type, such as
+\texttt{\{x y: a\} -> Witch (x * y ≡ y * x) a} where we make sure that \texttt{*}
+over \texttt{a} is commutative. However, it is unclear whether having all user's code
+under a monad-like structure would lead to well-structured code.
 
@@
 
+\section{Conclusion and Future Work}
+
+While it is hard to say whether we have achieve our goals before user
+evaluations, Witch steps towards a future where proof assistants are more
+friendly towards users, particularly newcomers.
+
 \end{document}

### 2020-09-18 paper/main.tex
more text

--- 2020-09-07 paper/main.tex
@@
-\documentclass[acmsmall]{acmart}
+\documentclass[sigconfl]{acmart}
 
@@
 \title[Towards user-friendliness in theorem provers]{Towards user-friendliness
-  in proof assistants: an effect-based attempt}
+  in proof assistants: automated strategies \textbf{via} algebraic effects and handlers}
 
-\author{April Gonçalves}
-\email{april@cyberglot.me}
-\affiliation{
-  \institution{Metastate AG}
-  \city{Edinburgh}
-  \state{UK}
-}
+% \author{April Gonçalves}
+% \email{april@metastate.dev}
+% \affiliation{
+%   \institution{Metastate}
+%   \city{Edinburgh}
+%   \state{UK}
+% }
 
-\renewcommand{\shortauthors}{April Gonçalves}
+% \renewcommand{\shortauthors}{April Gonçalves}
 
@@
 software. \textit{Our hypothesis is that programmers are well-equipped to derive and
-prove properties of their software, but they lack the mathematical maturity and
-vocabulary to carry on a formal proof. } We have evidence that students fail to
+prove properties of the software they write, but they lack the mathematical maturity and
+vocabulary to carry out a formal proof. } We have evidence that students fail to
 produce well-made proofs due to the lack of mathematical maturity, even though
@@
 under a shared interface, a proof object that can manipulate itself while
-querying different automated proof engines.
+enquiring different automated proof engines.
 
@@
   research languages, such as Koka, Eff, Frank and Effekt, what suggests a greater
-  potential to be investigated further.
+  potential.
 \end{enumerate}
@@
 
-The present project is still under development, and we intend to develop a core calculus and a
-full compiler-level implementation into the Juvix\footnote{Juvix is a
-  dependently-typed programming language for smart contracts. More information
-  at juvix.org} programming language.
+The present project intends to land itself as a compiler-level implementation into the
+Juvix\footnote{Juvix is a dependently-typed programming language for smart
+  contracts. More information at juvix.org} programming language. We design
+Juvix with focus on working programmers familiar with strongly-typed functional
+programming.
 
@@
    \centering
-    \includegraphics[width=\textwidth]{image/witch.eps}
-    \caption{Low-fidelity prototype of Witch}
+    \includegraphics[height=\textheight]{image/witch.eps}
+    \caption{Summary of Witch pertaining to strategies, examples
+      and the architecture.}
     \label{fig:prototype}
@@
 
-In this section, we introduce our tool, named Witch.
+In this section, we introduce our approach, named Witch\footnote{Our tool's name is
+  a play after assistant tools colloquially called ``wizards''. There is no
+  consensus of what a wizard is or what are exactly the tasks it is supposed
+  to help users. Wizards seem to be used mostly for multiple-step and/or
+  configuration features, however. We went for the name ``witch'' to align it to
+the idea of assistant tools, while dodging the overloaded, yet nebulous
+terminology.}. We define a \textit{witch} as an assistant tool for theorem
+provers that congregates many different strategies for proof automation. Our
+specification for a \textit{witch} for Juvix uses algebraic effects and handlers
+as the means to congregate strategies as effects.
 
-\paragraph{Downsides of our approach}
+\paragraph{Algebraic Effects and Handlers} Algebraic effects were introduced by
+**citation, and their handlers were introduced later on by **citation. An
+algebraic effect is defined by an effect signature that comprises a set of
+operations, and handlers that denote said operations. A handler may interpret
+operations at the compiler-level, which was formally named co-model, but
+colloquially called ``top-level handler''. Handlers are the most general form to
+denote a set of operation, and more specific classes of handlers also exist.
+
+\paragraph{The Essence of Witch}
+In Figure \ref{fig:prototype}, we sum up our \textit{witch} approach.
+As for the syntax, we use \texttt{operation \{ params \} via handler} that is an
+improvement over \texttt{handler(operation, params)}, since effect handling is similar
+to function application where it carries effect information as well.
+The user defines data types and functions as usual, and then uses a
+\textit{witch} to prove properties concerning said definitions. The Examples
+section in Figure \ref{fig:prototype} shows it in action. The examples are
+over-simplified to enable a clearer communication of our proposal -- we avoid
+more complex properties and complicated proofs as initial examples. The proof of
+commutativity of addition under natural numbers and of associativity of list
+concatenation are shown, and use the three main effects: Solver, Proof Search
+and Tactics. In the proof assistant literature, there exists no precise
+definition of commonly used terms ``solver'', ``proof search'' and ``tactics''.
+All said terms are used in different communities to mean ``automatic strategy to
+construct a term under certain constraints''. Here, however, we opt for a
+pragmatic differentiation:
+\begin{itemize}
+  \item The Solver effect is used for integration with external engines via IO;
+    we believe it suffices to say, e.g. \texttt{SMT}, as handlers should
+    implement internal strategies to choose between the so-called logics
+    within a solver. If the black-box approach to solvers presents itself a
+    challenge, an specialisation of the handler is possible, e.g.
+    \texttt{operation \{ params \} via Z3.QF-UFLIA}.
+  \item The Proof Search effect is used for library-level algorithms; users may
+    choose to implement their own algorithms using a limited set of
+    meta-programming constructs that are handled at top-level\footnote{The
+      meta-programming constructs are operations of the Typechecker effect
+      whose handlers are not available for the user.}.
+    \item The Tactics effect represent strategies that simplifies the proof at
+      least one step, and may not complete all proof goals. This style is mainly
+      employed in the proof assistant Coq. While we do not foresee as many
+      tactics implemented as in Coq, we believe famous tactics such as
+      \texttt{omega}, \texttt{ring}, \texttt{Admitted} are useful to users of
+      all levels of expertise.
+    \item Lastly, the Error effect represents feedback messages to the user,
+      since any of the strategies may fail. Error has two operations,
+      \texttt{throw} and \texttt{trace}: the former notifies the user a strategy
+      has failed, while the latter registers\footnote{Internally, the
+        Typechecker effect should have a tree that stores all currently
+        saved traces.} completed sub-goals during the
+      strategy's attempt to complete the proof.
+\end{itemize}
+
+\paragraph{Witch's Architecture}
+A \textit{witch} sits between the typechecker and the interactive mode of a
+proof assistant. It uses constructs provided by the typechecker and notifies the
+interactive mode with regards to the state of the current strategy attempted.
+The user may manipulate proof handlers by composing or writing their own.
+
+\paragraph{Downsides of our Approach}
 There are two main styles for writing proofs within a proof assistant: external
 verification and internal verification. The latter concerns itself with code
-that is \textit{correct-by-construction}, meaning that only valid states allowed and it
+that is \textit{correct-by-construction}, meaning that only valid states can be encoded and it
 carries all information necessary to make proofs trivial; while the former
-concerns itself with proofs about non-proof-carrying code.
+concerns itself with proofs about code that does not carry any additional
+information for proving purposes.
 Witch's primarily focus is on external verification. We believe that newcomers
@@
 write their code as they normally would do and then prove necessary properties.
-However, Witch does not support writing correct-by-construction code.
+Witch does not support writing correct-by-construction code. As proofs
+are erased during compilation-time in Juvix, Witch could be extended
+to be indexed by proof objects and parameterised over any type, such as
+\texttt{\{A: Type\} $\rightarrow$ x y: A $\rightarrow$ }
+\includegraphics[height=0.02\textheight]{image/hat.eps} \texttt{ (x * y $\equiv$
+  y * x) } where we make sure that \texttt{*} over \texttt{A} is commutative.
+However, it is unclear whether having user's code under a monad-like structure leads
+to well-structured code.
 
-\section{Witch in Agda} \label{witch-agda}
+\section{Agda's Witch} \label{witch-agda}
 
-\paragraph{Why Agda?} Agda provides high-level meta-programming constructs, and
-its coding style is a reminiscent of ML family of functional programming languages.
+\paragraph{Why Agda?} Agda provides higher-level meta-programming constructs, and
+its coding style is a reminiscent of the ML family of functional programming languages.
 
@@
 Agda. However, a solid implementation may not be trivial to achieve. In Agda,
-we translate all calls into optimised continuation-passing style that inlines
-all calls. This strategy also works at compiler-level if necessary. There are
+we translate effect handling into optimised continuation-passing style that inlines
+all applications. This strategy also works at compiler-level if necessary. There exist
 many strategies to efficiently implement algebraic effects and handlers, but we
@@
 
+\section{Related and Future Work}
+
+While it is hard to say whether we have achieve our goals before user
+evaluations, Witch steps towards a future where proof assistants are
+friendlier towards users, particularly newcomers. The present work is in its
+infancy, and there are many issues concerning Witch's ability to guide newcomers
+towards correct-by-construction software, which constitutes the main improvement
+we intend for Witch. We hypothesise about the possibility of using proof
+reconstruction, therefore relocating Witch to an assistant that lives solely
+within the interactive mode -- as opposed to a framework for proof
+automation in user code.
+
+In parallel with the usability work, we plan to develop a formalisation of Witch
+as a dependent typed language with effectful, dependently typed operations and
+effect handler, based on previous work on fibred algebraic effects.
+
 \end{document}

### 2020-09-18 paper/main.tex
related work

@@
 
-\title[Towards user-friendliness in theorem provers]{Towards user-friendliness
+\title[Towards user-friendliness in proof assistants]{Towards user-friendliness
   in proof assistants: automated strategies \textbf{via} algebraic effects and handlers}
@@
         Typechecker effect should have a tree that stores all currently
-        saved traces.} completed sub-goals during the
-      strategy's attempt to complete the proof.
+        saved traces.} completed sub-goals during the strategy's attempt to
+      complete the proof.
 \end{itemize}
@@
 
+\subsection{Comparison with Similar Approaches}
+
+\paragraph{Andromeda proof assistant} As mentioned, this project was inspired by the
+Andromeda proof assistant. It follows the LCF tradition of theorem provers,
+where there exist two distinct languages. One habits a safe nucleus that
+verifies hypotheses, on the other hand, the second hand comprises a polymorphic
+$\lambda$ calculus where users implement their theories and relay the
+verification to the nucleus.
+
+\paragraph{Meta-F*} F* is a dependently typed language with (monadic) effects and liquid
+types. For tactics, F* uses a library called Meta-F*, where tactics are
+considered an effect that uses meta-programming provided by the typechecker to
+manipulate proof objects. Agda's Witch implementation is heavily inspired by Meta-F*.
+
+\paragraph{Mtac and Cybele} The idea of proof strategies happening within an
+effectful structure was first introduced in Cybele and later extended into Mtac.
+Mtac extends Coq's powerful main language, providing the user with a
+dependently-typed tactic language.
+
+\subsection{Improving Witch Further}
 While it is hard to say whether we have achieve our goals before user

### 2020-09-18 paper/main.tex

@@
 
+\newcommand{\comment}[1]{\footnote{Comment:~#1}}
 \usepackage{pdfpages}
@@
 \begin{abstract}
-Proof assistants provide a framework for modelling and verification of
-theories, as well as trust-worthy software. However, such power is usually only
+Proof assistants provide a framework for the modelling and verification of
+theories, as well as trustworthy software. However, such power is usually only
 available to experts. We propose a new approach, based on algebraic effects and
-handlers, to integrate different automated proof strategies that enables
-newcomers to take advantage of proof assistants without a more in-depth
-understanding of underlying theory. Our approach gives beginner users an effect
-system, a handful of effectful strategies (tactics, proof search and a SMT
-solver) and their handlers under a shared interface, while advanced users can
+handlers, to integrate different automated proof strategies that enable
+newcomers to take advantage of proof assistants without an in-depth
+understanding of underlying theory. Our approach gives newcomers an effect
+system, a handful of effectful strategies (tactics, proof search, and SMT
+solvers) and their handlers under a shared interface, while advanced users can
 extend our system with new effects and new handlers. Lastly, we prototype the
 system as a library in Agda. While our prototype is minimal, it shows how easily
-proofs can be carried on so long as the user has the correct intuition. We
+proofs can be carried out so long as the user has the correct intuition. We
 believe our system empowers non-experts and has the potential to bring verified
@@
 enables such assistants to exist. Coq and Isabelle/HOL are more commonly applied
+\comment{I'm unsure what ``that frequently matches a deeper understanding of
+  Type Theory'' means... I~assumed the domain knowledge you meant \emph{was}
+  type theory, and perhaps the details of the specific proof assistant.}
 outside their niche, and their programming style is sharply different from
@@
 held for a proof assistant, however there exists studies that account for
-an informal ``usability'' criteria -- they appear to measure how fast users can
+informal ``usability'' criteria -- they appear to measure how fast users can
+\comment{Usage of ``appear'' seems like you're gonna really shit on these studies?}
 familiarise themselves with the system or IDE.
 
-Folklore within the proof assistants community seems to show that typical users
-find Coq hard to use due to a large library of tactics and difficult readability
-of the code after its completion. Many Coq learning materials suggest users to
+Folklore within the proof assistants community says that newcomers
+find Coq hard to use due to a large library of tactics and difficulty reading
+the code after its completion. Many Coq learning materials suggest that users
 add comments for structural induction cases and inductive hypothesis. As
 mentioned, no user studies were conducted to attest such hypotheses.
+\comment{Double use of hypothesis with different denotations is confusing.}
 
-It also has to be granted that proof assistants are relatively new technology
+Granted, proof assistants are a relatively new technology
 and there are no guidelines or even an intuition on how such systems should
 perform or what features should be available to the users. The closest model we
-have are proofs by hand, however, following that model for proof assistants has
-two main pitfalls: (a) proofs by hand are also not widely taught in mathematics
-classes during school years; and (b) proofs by hand and automated proof
-writing employ fundamentally different paradigms, where the latter requires
+\comment{Not sure what you mean by ``perform'', do you mean ``work/function''?}
+have are proofs by hand. However, following that model for proof assistants has
+two main pitfalls: (a) proofs by hand are not widely taught outside of
+university mathematics courses; and (b) proof by hand and automated proof
+employ fundamentally different paradigms, where the latter requires
 axioms and formulations to be encoded explicitly, commonly known as a ``pedantic
@@
 
-To popularise software verification, we mush make proof writing less of a
+To popularise software verification, we must make proof writing less of a
 burden to the user. Currently, only specialists can write proofs for their
-programs, even though the working programmer understands the domain and
+programs, even though the working programmer surely understands the domain and
 invariants of their projects -- otherwise they would not be able to write any
@@
 prove properties of the software they write, but they lack the mathematical maturity and
-vocabulary to carry out a formal proof. } We have evidence that students fail to
+vocabulary to carry out a formal proof.} We have evidence that students fail to
 produce well-made proofs due to the lack of mathematical maturity, even though
@@
 
-In our approach, we propose an (algebraic) effects and handlers view of such
-proofs, based on prior work developed by the Andromeda proof assistant. Here,
+In our approach, we propose an effects and handlers view of such
+proofs, based on prior work developed on the Andromeda proof assistant. Here,
 our users will program as they would normally and invoke
-a proof environment as an effect to prove certain properties as they go. Given
+the proof environment as an effect to prove certain properties as they go. Given
 that the proof environment is \textit{just} an effect, we envision that different proof
-styles (e.g, Agda-style dependent types, SMT solver, proof search) can be ``composed''
+styles (e.g., Agda-style dependent types, SMT solver, proof search) can be ``composed''
 under a shared interface, a proof object that can manipulate itself while
-enquiring different automated proof engines.
+querying different automated provers.
 
-The reasons we employ algebraic effects and handlers are manifold:
+The reasons we employ algebraic effects and handlers are numerous:
 \begin{enumerate}
 \item as proofs cannot be fully automated, all approaches that try to automate
-  the process (e.g, proof search, SMT solver) may either be non-deterministic or
+  the process (e.g, proof search, SMT solver) may be non-deterministic or
   never find a solution. Therefore, the system should be able to handle
@@
   intricate effects machinery such as monad transformers;
-\item its semantics accommodate composition of arbitrary effects and the
+\item the semantics of effects and handlers accommodate composition of arbitrary effects and the
   composition of multiple handlers, which means users have the ability to weaken
   more general strategies into specific ones while maintaining the original untouched;
-\item it has well-defined semantics, and it is the main feature of many new
-  research languages, such as Koka, Eff, Frank and Effekt, what suggests a greater
+  \comment{Not sure what you mean by ``original'' here?}
+\item effects and handlers have well-defined semantics, and it is the main feature of many new
+  research languages, such as Koka, Eff, Frank and Effekt, which suggests a greater
   potential.
+  \comment{You may need to explain that potential; does it result from the
+    prediction that more programmers will be familiar with effects in the
+    future, due to their popularity?}
 \end{enumerate}
@@
 
-The present project intends to land itself as a compiler-level implementation into the
+The present project intends to be a compiler-level implementation as part of the
 Juvix\footnote{Juvix is a dependently-typed programming language for smart
-  contracts. More information at juvix.org} programming language. We design
-Juvix with focus on working programmers familiar with strongly-typed functional
+  contracts. More information at juvix.org} programming language. Juvix is designed
+with focus on working programmers familiar with strongly-typed functional
 programming.
@@
 code without investing time into learning dependent types and theorem proving.
-The project's goals are presented as follows:
+The project's goals are to:
 \begin{enumerate}
@@
 
-\paragraph{Contributions} While the project is a work-in-progress, this paper
-provides three important contributions that lays out the full extent of the
-work, which are presented as follows:
+\paragraph{Contributions} The project is a work-in-progress, but this paper
+makes three important contributions that pave the way for the full implementation:
 \begin{enumerate}
@@
   (Section \ref{witch-agda});
-\item a short technical account of the effort required to materialise such a
-  user interface into proof assistants (Section \ref{tech-details}).
+\item a short technical account of the effort required to implement such a
+  user interface for proof assistants (Section \ref{tech-details}).
 \end{enumerate}
@@
 In this section, we introduce our approach, named Witch\footnote{Our tool's name is
-  a play after assistant tools colloquially called ``wizards''. There is no
-  consensus of what a wizard is or what are exactly the tasks it is supposed
-  to help users. Wizards seem to be used mostly for multiple-step and/or
+  a play on the assistant tools colloquially called ``wizards''. There is no
+  consensus of what a wizard is or what exactly the tasks are it is supposed
+  assist with. Wizards seem to be used mostly for multiple-step and/or
   configuration features, however. We went for the name ``witch'' to align it to
   the idea of assistant tools, while dodging the overloaded, yet nebulous
-terminology.}. We define a \textit{witch} as an assistant tool for theorem
-provers that congregates many different strategies for proof automation. Our
+  terminology.}. We define a \textit{witch} as an assistive tool for theorem
+provers which congregates many different strategies for proof automation. Our
 specification for a \textit{witch} for Juvix uses algebraic effects and handlers
-as the means to congregate strategies as effects.
+as the means of congregation.
 
@@
 denote a set of operation, and more specific classes of handlers also exist.
+\comment{I'm pretty confused by the past few sentences.}
 
@@
 In Figure \ref{fig:prototype}, we sum up our \textit{witch} approach.
-As for the syntax, we use \texttt{operation \{ params \} via handler} that is an
+As for the syntax, we use \texttt{operation \{ params \} via handler}, which is an
 improvement over \texttt{handler(operation, params)}, since effect handling is similar
-to function application where it carries effect information as well.
+to function application, but also carries effect information.
 The user defines data types and functions as usual, and then uses a
-\textit{witch} to prove properties concerning said definitions. The Examples
-section in Figure \ref{fig:prototype} shows it in action. The examples are
-over-simplified to enable a clearer communication of our proposal -- we avoid
-more complex properties and complicated proofs as initial examples. The proof of
+\textit{witch} to prove properties about said definitions. The Examples
+section in Figure \ref{fig:prototype} shows this in action. The examples are
+simplified for the sake of clarity -- we avoid
+more complex properties and complicated proofs. The proof of
 commutativity of addition under natural numbers and of associativity of list
@@
 definition of commonly used terms ``solver'', ``proof search'' and ``tactics''.
-All said terms are used in different communities to mean ``automatic strategy to
-construct a term under certain constraints''. Here, however, we opt for a
-pragmatic differentiation:
+All these terms are used in different communities, and mean some variation of ``automatic strategy to
+construct a term under certain constraints''. Here, however, we use the
+\comment{Not technically ``construct a term'', e.g., F* and Liquid Haskell's use
+  of SMT solvers never constructs any term.}
+following definitions:
 \begin{itemize}
-  \item The Solver effect is used for integration with external engines via IO;
-    we believe it suffices to say, e.g. \texttt{SMT}, as handlers should
-    implement internal strategies to choose between the so-called logics
-    within a solver. If the black-box approach to solvers presents itself a
-    challenge, an specialisation of the handler is possible, e.g.
+  \item The Solver effect is used for integration with external solvers via IO;
+    we believe should suffice for the user to write, e.g. \texttt{SMT}, and handlers should
+    implement internal strategies to choose between the different theories
+    supported by solvers. If the black-box approach to solvers presents itself a
+    challenge, a specialisation of the handler is possible, e.g.
     \texttt{operation \{ params \} via Z3.QF-UFLIA}.
@@
       whose handlers are not available for the user.}.
-    \item The Tactics effect represent strategies that simplifies the proof at
+    \comment{You essentially mean ``reflection'' here, right? You may want to
+      use that word, or ``quoting'', or whatnot, explicitly.}
+  \item The Tactics effect is used for strategies that simplify the goal at
     least one step, and may not complete all proof goals. This style is mainly
-      employed in the proof assistant Coq. While we do not foresee as many
-      tactics implemented as in Coq, we believe famous tactics such as
+    used in the proof assistant Coq. While we do not foresee using as many as many
+    tactics implemented as in Coq, we believe tactics such as
     \texttt{omega}, \texttt{ring}, \texttt{Admitted} are useful to users of
     all levels of expertise.
-    \item Lastly, the Error effect represents feedback messages to the user,
+    \comment{All three of these tactics are total, so you may want to use
+      examples which can fail or return partial proofs, such as \texttt{eauto}.}
+  \item Lastly, the Error effect is used for feedback to the user,
     since any of the strategies may fail. Error has two operations,
-      \texttt{throw} and \texttt{trace}: the former notifies the user a strategy
+    \texttt{throw} and \texttt{trace}: the former notifies the user that a strategy
     has failed, while the latter registers\footnote{Internally, the
       Typechecker effect should have a tree that stores all currently
-        saved traces.} completed sub-goals during the strategy's attempt to
-      complete the proof.
+      saved traces.} completed sub-goals during the
+    strategy's attempt to complete the proof.
 \end{itemize}
@@
 A \textit{witch} sits between the typechecker and the interactive mode of a
-proof assistant. It uses constructs provided by the typechecker and notifies the
-interactive mode with regards to the state of the current strategy attempted.
+proof assistant. It uses constructs provided by the typechecker and communicates
+with the interactive mode about the state of the current attempted strategy.
+\comment{Perhaps rephrase this sentence, as it's a bit unclear?}
 The user may manipulate proof handlers by composing or writing their own.
@@
 There are two main styles for writing proofs within a proof assistant: external
-verification and internal verification. The latter concerns itself with code
-that is \textit{correct-by-construction}, meaning that only valid states can be encoded and it
-carries all information necessary to make proofs trivial; while the former
-concerns itself with proofs about code that does not carry any additional
-information for proving purposes.
+verification and internal verification. The latter encourages code
+\comment{Consider using extrinsic versus intrinsic.}
+that is \textit{correct-by-construction}, meaning only valid states can be
+encoded and values carry all information necessary to make proofs trivial; while
+the former encourages writing code as usual, and reconstructing information
+needed for proofs only when necessary.
 Witch's primarily focus is on external verification. We believe that newcomers
@@
   y * x) } where we make sure that \texttt{*} over \texttt{A} is commutative.
+\comment{Sentence is confusing, please rephrase?}
 However, it is unclear whether having user's code under a monad-like structure leads
 to well-structured code.
+\comment{Sentence is confusing, please rephrase?}
 
@@
 
-Although Witch is implementable at the library level, it requires that proof
-assistants to provide a set of off-the-shelf features. The most important
-feature is type-level meta-programming. Witch is only possible given the proof
-assistant's ability to manipulate its own proof terms to generate new variables,
-holes, goals, among others and manipulate terms and types in a proof-carrying
-fashion. Secondly, the proof assistant should feature an interface with the
-outside world. Although it is not inherently a requirement, its absence means
-that no solver will be integrated, diminishing the proposed value of the tool.
-Lastly, proof assistants must support algebraic effects and handlers. If there
+Although Witch can be implemented as a library, it requires certain features
+from the proof assistant. The most important feature is type-level
+meta-programming: Witch requires that the proof assistant can manipulate its own
+proof terms, generate new variables, holes, goals, among others, and manipulate
+terms and types in a type-safe fashion.
+Secondly, the proof assistant should provide an interface to the outside world
+while type checking
+It is not essential, its absence means that no external solver can be
+integrated, diminishing the value of the tool.
+Lastly, the proof assistant must support algebraic effects and handlers. If there
 is no built-in solution, a library-level solution is possible -- as we did in
@@
 we translate effect handling into optimised continuation-passing style that inlines
-all applications. This strategy also works at compiler-level if necessary. There exist
-many strategies to efficiently implement algebraic effects and handlers, but we
-went for the one that seemed the most straight-forward method to implement it in Agda.
+all applications. This strategy can also be implemented at the compiler-level,
+if necessary. There are many strategies to efficiently implement algebraic effects and handlers, but we
+opted for the one that seemed the most straight-forward method to implement it in Agda.
 
@@
 \subsection{Improving Witch Further}
-While it is hard to say whether we have achieve our goals before user
-evaluations, Witch steps towards a future where proof assistants are
-friendlier towards users, particularly newcomers. The present work is in its
-infancy, and there are many issues concerning Witch's ability to guide newcomers
+While it is hard to say whether we have achieved our goals before user
+evaluations, Witch is a first step towards a future where proof assistants are
+friendlier to users, particularly newcomers. The present work is in its
+infancy, and there are many open problems regarding Witch's ability to guide newcomers
 towards correct-by-construction software, which constitutes the main improvement
-we intend for Witch. We hypothesise about the possibility of using proof
+we intend for Witch.
+
+We hypothesise possibility of using proof
 reconstruction, therefore relocating Witch to an assistant that lives solely
@@
 automation in user code.
+\comment{You should rephrase this -- it isn't a matter of proof reconstruction
+  per se, since most strategies generate proof objects in the compiler. Instead,
+it's a matter of inserting these objects into the source files. Note that this
+makes the proofs more brittle, since one advantage of tactics is that if your
+data types change slightly, proofs don't necessarily break, but instead your
+solver may compute a difference solution.}
 

### 2020-09-18 paper/main.tex
addresses comments

@@
 
-\newcommand{\comment}[1]{\footnote{Comment:~#1}}
 \usepackage{pdfpages}
@@
 The usability of proof assistants such as Coq, Agda, Isabelle/HOL and Twelf is
-hard to measure: all of them require significant domain knowledge that
-frequently matches a deeper understanding of Type Theory, the theory that
-enables such assistants to exist. Coq and Isabelle/HOL are more commonly applied
-\comment{I'm unsure what ``that frequently matches a deeper understanding of
-  Type Theory'' means... I~assumed the domain knowledge you meant \emph{was}
-  type theory, and perhaps the details of the specific proof assistant.}
-outside their niche, and their programming style is sharply different from
+hard to measure: all of them require significant domain knowledge in type
+theory, the theory that enables such assistants to exist. Coq and Isabelle/HOL
+are more commonly applied outside their niche, and their programming style is
+sharply different from
 mainstream programming and even functional programming. Granted, they come with
@@
 informal ``usability'' criteria -- they appear to measure how fast users can
-\comment{Usage of ``appear'' seems like you're gonna really shit on these studies?}
 familiarise themselves with the system or IDE.
@@
 the code after its completion. Many Coq learning materials suggest that users
-add comments for structural induction cases and inductive hypothesis. As
-mentioned, no user studies were conducted to attest such hypotheses.
-\comment{Double use of hypothesis with different denotations is confusing.}
+add code comments for structural induction cases and inductive hypothesis. As
+mentioned, no user studies were conducted to attest that such strategy improves
+the perceived quality of Coq proofs.
 
@@
 and there are no guidelines or even an intuition on how such systems should
-perform or what features should be available to the users. The closest model we
-\comment{Not sure what you mean by ``perform'', do you mean ``work/function''?}
+work or what features should be available to the users. The closest model we
 have are proofs by hand. However, following that model for proof assistants has
@@
   composition of multiple handlers, which means users have the ability to weaken
-  more general strategies into specific ones while maintaining the original untouched;
-  \comment{Not sure what you mean by ``original'' here?}
+  more general strategies into specific ones while maintaining top-level
+  handlers unmodified;
 \item effects and handlers have well-defined semantics, and it is the main feature of many new
   research languages, such as Koka, Eff, Frank and Effekt, which suggests a greater
-  potential.
-  \comment{You may need to explain that potential; does it result from the
-    prediction that more programmers will be familiar with effects in the
-    future, due to their popularity?}
+  potential due to their popularity.
 \end{enumerate}
@@
 **citation, and their handlers were introduced later on by **citation. An
-algebraic effect is defined by an effect signature that comprises a set of
+algebraic effect is defined by a set of
 operations, and handlers that denote said operations. A handler may interpret
@@
 colloquially called ``top-level handler''. Handlers are the most general form to
-denote a set of operation, and more specific classes of handlers also exist.
-\comment{I'm pretty confused by the past few sentences.}
+denote a set of operations, and less general classes of handlers also exist.
 
@@
 definition of commonly used terms ``solver'', ``proof search'' and ``tactics''.
-All these terms are used in different communities, and mean some variation of ``automatic strategy to
-construct a term under certain constraints''. Here, however, we use the
-\comment{Not technically ``construct a term'', e.g., F* and Liquid Haskell's use
-  of SMT solvers never constructs any term.}
-following definitions:
+All these terms are used in different communities, and mean some variation of
+``automatic strategy to construct a term under certain constraints''. Here,
+however, we use the following definitions:
 \begin{itemize}
@@
     choose to implement their own algorithms using a limited set of
-    meta-programming constructs that are handled at top-level\footnote{The
+    meta-programming\footnote{By meta-programming, we mean ``code that manipulates
+    itself'', and not ``programming that happens in a higher level of abstraction''.
+    For dependently typed programming languages, the usual term is reflection.
+    However, we prefer not use reflection since it has another meaning in
+    terms of effectful computations.} constructs that are handled at top-level\footnote{The
       meta-programming constructs are operations of the Typechecker effect
       whose handlers are not available for the user.}.
-    \comment{You essentially mean ``reflection'' here, right? You may want to
-      use that word, or ``quoting'', or whatnot, explicitly.}
   \item The Tactics effect is used for strategies that simplify the goal at
@@
     tactics implemented as in Coq, we believe tactics such as
-    \texttt{omega}, \texttt{ring}, \texttt{Admitted} are useful to users of
+    \texttt{eauto}, \texttt{??}, \texttt{??} are useful to users of
     all levels of expertise.
-    \comment{All three of these tactics are total, so you may want to use
-      examples which can fail or return partial proofs, such as \texttt{eauto}.}
     \item Lastly, the Error effect is used for feedback to the user,
@@
 A \textit{witch} sits between the typechecker and the interactive mode of a
-proof assistant. It uses constructs provided by the typechecker and communicates
-with the interactive mode about the state of the current attempted strategy.
-\comment{Perhaps rephrase this sentence, as it's a bit unclear?}
+proof assistant. It uses meta-programming constructs provided by the typechecker and notifies
+the interactive mode about whether the current attempted strategy was successful.
 The user may manipulate proof handlers by composing or writing their own.
@@
 verification and internal verification. The latter encourages code
-\comment{Consider using extrinsic versus intrinsic.}
 that is \textit{correct-by-construction}, meaning only valid states can be
@@
 \includegraphics[height=0.02\textheight]{image/hat.eps} \texttt{ (x * y $\equiv$
-  y * x) } where we make sure that \texttt{*} over \texttt{A} is commutative.
-\comment{Sentence is confusing, please rephrase?}
-However, it is unclear whether having user's code under a monad-like structure leads
-to well-structured code.
-\comment{Sentence is confusing, please rephrase?}
+  y * x) }.
 
@@
 all applications. This strategy can also be implemented at the compiler-level,
-if necessary. There are many strategies to efficiently implement algebraic effects and handlers, but we
-opted for the one that seemed the most straight-forward method to implement it in Agda.
+if necessary. There are many strategies to efficiently implement algebraic
+effects and handlers, but we opted for the one that seemed the most
+straight-forward method to implement it in Agda.
 
@@
 towards correct-by-construction software, which constitutes the main improvement
-we intend for Witch.
-
-We hypothesise possibility of using proof
-reconstruction, therefore relocating Witch to an assistant that lives solely
+we intend for Witch. We hypothesise possibility of inserting into the source
+code a  \textit{proof sketch} that contains sub-goals of interest for the user and guides the
+typechecker to rebuild the derivation tree faster. This change would, therefore,
+relocate Witch to an assistant that lives solely
 within the interactive mode -- as opposed to a framework for proof
-automation in user code.
-\comment{You should rephrase this -- it isn't a matter of proof reconstruction
-  per se, since most strategies generate proof objects in the compiler. Instead,
-it's a matter of inserting these objects into the source files. Note that this
-makes the proofs more brittle, since one advantage of tactics is that if your
-data types change slightly, proofs don't necessarily break, but instead your
-solver may compute a difference solution.}
+automation in user code. The implementation of such feature may present itself
+as a challenge, however.
 

### 2020-09-19 paper/main.tex
add final version

@@
 believe our system empowers non-experts and has the potential to bring verified
-software to many relevant industries, such as finance.
+software to relevant industries, such as finance.
 \end{abstract}
@@
 
-The usability of proof assistants such as Coq, Agda, Isabelle/HOL and Twelf is
+The usability of proof assistants such as Coq \cite{DBLP:journals/corr/abs-cs-0603118} and Agda
+\cite{DBLP:conf/tldi/Norell09} is
 hard to measure: all of them require significant domain knowledge in type
 theory, the theory that enables such assistants to exist. Coq and Isabelle/HOL
-are more commonly applied outside their niche, and their programming style is
+are more commonly applied outside their niche
+\cite{DBLP:journals/corr/abs-1907-10674, peltier:hal-01562944}, and their programming style is
 sharply different from
 mainstream programming and even functional programming. Granted, they come with
-their own integrated development environment (IDE), which may make it easier for
+their own integrated development environment (IDE)
+\cite{DBLP:journals/sttt/FaithfullBTT18, DBLP:conf/itp/RoeS16}, which may make it easier for
 students and newcomers. To our knowledge, no usability study has been
@@
 informal ``usability'' criteria -- they appear to measure how fast users can
-familiarise themselves with the system or IDE.
+familiarise themselves with the system or IDE \cite{Wiedijk2003,
+  DBLP:journals/corr/abs-1808-09701}.
 
@@
 find Coq hard to use due to a large library of tactics and difficulty reading
-the code after its completion. Many Coq learning materials suggest that users
+the code after its completion. Coq learning materials, such as ``Software
+Foundations'' by Pierce \textit{et al},  suggest that users
 add code comments for structural induction cases and inductive hypothesis. As
@@
 two main pitfalls: (a) proofs by hand are not widely taught outside of
-university mathematics courses; and (b) proof by hand and automated proof
+college-level mathematics courses \cite{Anapa2010}; and (b) proof by hand and automated proof
 employ fundamentally different paradigms, where the latter requires
-axioms and formulations to be encoded explicitly, commonly known as a ``pedantic
-proof style''.
+axioms and formulations to be encoded explicitly.
 
@@
 produce well-made proofs due to the lack of mathematical maturity, even though
-they do understand the subject matter at hand.
+they do understand the subject matter at hand \cite{Knobelsdorf2017, Knobelsdorf2016}.
 
 In our approach, we propose an effects and handlers view of such
-proofs, based on prior work developed on the Andromeda proof assistant. Here,
+proofs, based on prior work developed on the Andromeda proof assistant \cite{Bauer2018}. Here,
 our users will program as they would normally and invoke
@@
 that the proof environment is \textit{just} an effect, we envision that different proof
-styles (e.g., Agda-style dependent types, SMT solver, proof search) can be ``composed''
+styles (e.g., Agda-style dependent types , SMT solver, proof search) can be ``composed''
 under a shared interface, a proof object that can manipulate itself while
@@
 \item effects and handlers have well-defined semantics, and it is the main feature of many new
-  research languages, such as Koka, Eff, Frank and Effekt, which suggests a greater
+  research languages, such as Koka \cite{Leijen2017}, Eff \cite{Bauer2012},
+  Frank \cite{DBLP:journals/jfp/ConventLMM20} and Effekt
+  \cite{DBLP:journals/jfp/BrachthauserSO20}, which suggests a greater
   potential due to their popularity.
@@
   strategies, and also user-defined handlers for existing effects (Section \ref{intro-witch});
-\item a minimal prototype in Agda that validates the feasibility of such system
-  (Section \ref{witch-agda});
 \item a short technical account of the effort required to implement such a
-  user interface for proof assistants (Section \ref{tech-details}).
+  user interface for proof assistants via a a minimal prototype in Agda that
+  validates the feasibility of such system  (Section \ref{tech-details}).
 \end{enumerate}
@@
 \paragraph{Algebraic Effects and Handlers} Algebraic effects were introduced by
-**citation, and their handlers were introduced later on by **citation. An
+Plotkin \textit{et al} \cite{Plotkin2003}, and their handlers were introduced later on by
+Plotkin \& Pretnar \cite{Plotkin2013}. An
 algebraic effect is defined by a set of
@@
 colloquially called ``top-level handler''. Handlers are the most general form to
-denote a set of operations, and less general classes of handlers also exist.
+denote a set of operations, and less general classes of handlers also exist
+\cite{DBLP:conf/esop/AhmanB20}.
 
@@
     challenge, a specialisation of the handler is possible, e.g.
-    \texttt{operation \{ params \} via Z3.QF-UFLIA}.
+    \texttt{operation \{ params \} via Z3.QF-UFLIA} \cite{Z32008}.
   \item The Proof Search effect is used for library-level algorithms; users may
@@
     tactics implemented as in Coq, we believe tactics such as
-    \texttt{eauto}, \texttt{??}, \texttt{??} are useful to users of
+    \texttt{eauto}, \texttt{rewrite}, \texttt{unfold} are useful to users of
     all levels of expertise.
@@
 to be indexed by proof objects and parameterised over any type, such as
-\texttt{\{A: Type\} $\rightarrow$ x y: A $\rightarrow$ }
+\texttt{$\forall $ \{A: Type\} (x y: A) $\rightarrow$ }
 \includegraphics[height=0.02\textheight]{image/hat.eps} \texttt{ (x * y $\equiv$
@@
 
-\section{Agda's Witch} \label{witch-agda}
-
-\paragraph{Why Agda?} Agda provides higher-level meta-programming constructs, and
-its coding style is a reminiscent of the ML family of functional programming languages.
-
-\subsection{Technical Effort Required} \label{tech-details}
+\section{Technical Effort Required and Prototype in Agda} \label{tech-details}
 
@@
 is no built-in solution, a library-level solution is possible -- as we did in
-Agda. However, a solid implementation may not be trivial to achieve. In Agda,
+Agda. However, a solid implementation may not be trivial to achieve.
+
+In Agda,
 we translate effect handling into optimised continuation-passing style that inlines
@@
 
+\paragraph{Why Agda?} Agda provides higher-level meta-programming constructs, and
+its coding style is a reminiscent of the ML family of functional programming
+languages. Agda's meta-programming constructs are built-in and a monadic
+interface is available under the module \texttt{TC} within the standard library.
+
 \section{Related and Future Work}
@@
 \paragraph{Andromeda proof assistant} As mentioned, this project was inspired by the
-Andromeda proof assistant. It follows the LCF tradition of theorem provers,
+Andromeda proof assistant \cite{Bauer2018, DBLP:conf/icms/BauerHP20}. It follows the LCF tradition of theorem provers,
 where there exist two distinct languages. One habits a safe nucleus that
@@
 \paragraph{Meta-F*} F* is a dependently typed language with (monadic) effects and liquid
-types. For tactics, F* uses a library called Meta-F*, where tactics are
+types. For tactics, F* uses a library called Meta-F* \cite{MetaFstar}, where tactics are
 considered an effect that uses meta-programming provided by the typechecker to
@@
 \paragraph{Mtac and Cybele} The idea of proof strategies happening within an
-effectful structure was first introduced in Cybele and later extended into Mtac.
+effectful structure was first introduced in Cybele \cite{Claret2013} and later extended into Mtac \cite{Ziliani2013}.
 Mtac extends Coq's powerful main language, providing the user with a
@@
 as a dependent typed language with effectful, dependently typed operations and
-effect handler, based on previous work on fibred algebraic effects.
+effect handler, based on previous work on fibred algebraic effects
+\cite{DBLP:journals/pacmpl/Ahman18}.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{main}
 

### 2021-06-26 paper/main.tex
add paper
spelling remove duplicated a

@@
 \item a short technical account of the effort required to implement such a
-  user interface for proof assistants via a a minimal prototype in Agda that
+  user interface for proof assistants via a minimal prototype in Agda that
   validates the feasibility of such system  (Section \ref{tech-details}).
